Contribution Title\thanks{Supported by organization x.}

### 2019-11-10 sections/evaluation.tex
add length comparsion and proof size graphs

\begin{center}
\begin{tabular}{ | m{3.5cm} | m{2cm}| m{2cm} | m{2cm} | m{2.5cm} | } 
\hline
Solver & \# solved & PAR-2 & Clause Size & Cl Reduction\% \\ 
\hline
$\MapleBase$ & cell5 & cell6 & 59.3 & 37.53\% \\ 
\hline
$\MapleIUIPPURE$ & 221 & cell9 & cell10 & cell11\\ 
\hline
$\MapleIUIMIN$ & 226 & cell9 & 41.5 & 49.5\%\\ 
\hline
\end{tabular}
\end{center}

>>>>

\begin{center}
\begin{tabular}{ | m{3.5cm} | m{2cm}| m{2cm} | m{2cm} | m{2.5cm} | } 
\hline
Solver & \# solved & PAR-2 & Clause Size & Cl Reduction\% \\ 
\hline
$\MapleBase$ & 221 & 5005.2 & 62.6 & 36.53\% \\ 
\hline
$\MapleIUIPPURE$ & cell9 & cell9 & cell10 & cell11\\ 
\hline
$\MapleIUIMIN$ & 226 & 4933.6 & 45.2 & 47.5\%\\ 
\hline
\end{tabular}
\end{center}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth, natwidth=610,natheight=642]{clause_length_PDF.png}
    \caption{Average clause (relative to 1-UIP clauses) size distribution. X axis indicates the relative size difference, and Y axis indicates the PDF.}
     \label{fig:len_pdf}
\end{figure}
\begin{figure} \label{fig:len_compare}
    \centering
    \includegraphics[width=0.8\textwidth, natwidth=610,natheight=642 ]{i-uip-sizes-compare.png}
    \caption{Average clause size comparison plot. Each point in the plot represents an benchmark instance. X and Y axis shows the clause length from $\MapleIUIMIN$ and $\MapleBase$, respectively  }
    \label{fig:len_compare}
\end{figure}
